Application for Rethinking Foundations of Physics 2017

### 2017-01-15 Rethinking Foundations of Physics 2017/application.tex
application.tex Updating...

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. This raises an important philosophical question with
immense practical relevance in the context of quantum computing. The
question is whether there is a ``real'' infinitely-precise quantum
state that is being approximated and that can be more and more accurately
described given more and more resources.

@@

Although a family of more and more precise quantum IVPMs might be
induced from a real quantum state, given a particular quantum IVPM,
i.e., using a particular measurement apparatus, our investigation
leaves an open question of whether behind it there exists a ``real''
state. There are several possibilities.

One possibility is to trace back the original definition of a quantum
state. A quantum state could be formulated as a density matrix in
von Neumann's formalism~\cite{vonNeumann1955,Varadarajan2008}. Later,
Mackey defined a quantum state as additive probability measure as
we did in definition~\ref{def:QuantumProbabilitySpace}~\cite{inun.606849520040101,Varadarajan2008}.
Although Gleason proved Mackey states are von Neumann states in dimension
$\ge3$, it might not have to be when we generalized Mackey states
to quantum IVPMs, and maybe we should use quantum IVPMs as the most
primitive definition of states.

The other possibility focus on the meaning of the probability. Since
a quantum IVPM cannot be defined without consider a particular measurement
apparatus, and the information extracted from this apparatus, the
interval-valued probability itself could be considered subjective,
and could be interpreted in the Bayesian sense as ``lack of knowledge''.
This, and similar arguments elegantly expressed by recent work on
Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which
suggests that the quantum state is more like an interactive system
in computer science parlance. In other words, the state is only determined
by its interactions with the environment or observers. A rough but
useful analogy in the context of computer science would be a web server:
the state of such a system cannot be said to exist independently of
the interactions with clients; each interaction with a client determines
a future state of the system and may affect future interactions. Crucially,
each client may have a \emph{different} view of the web server that
is consistent with their own history of interactions. This computational
perspective agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
that asserts that the quantum state is subjective: each observer has
a different view of the quantum system that is consistent with their
previous observations and that allows that observer, independently
of other observers, to assign beliefs (i.e., probabilities) to possible
future interactions.

>>>>

Quantum machines is a theory of probability, which is computed by
the Born rule~\cite{Born1983,Mermin2007,Jaeger2007} and is used
to be considered as infinite precise and objective. If we insist that
probabilities cannot be computed to infinite precision, we should
change the quantum probability to a subjective probability model,
which is bound to be approximations represented by intervals of confidence.
Following this idea, quantum states themselves can only be discussed
within intervals of confidence. This raises an important philosophical
question, whether there is a ``real'' infinitely-precise quantum
state that is being approximated and that can be more and more accurately
described given more and more resources.

Mathematically, this idea might require us to reformulate the very
definition of a quantum state. A quantum state could be defined as
a density matrix in von Neumann's formalism~\cite{vonNeumann1955,Varadarajan2008}.
Later, Mackey defined a quantum state as additive probability measure
as we did in definition~\ref{def:QuantumProbabilitySpace}~\cite{inun.606849520040101,Varadarajan2008}.
Although Gleason proved Mackey states are von Neumann states in dimension
$\ge3$, when we generalized Mackey states to quantum interval-valued
probability measures (IVPM), a quantum IVPM may not correspond to
any density matrix as in example~\ref{ex:three-dimensional-three-value}
and \ref{ex:three-dimensional-4-value}. In this situation, we could
consider quantum IVPMs as the most primitive definition of quantum
states to reconstruct the whole quantum machines. Or we might follow
the idea of Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}
to formulate a quantum state as an interactive system in computer
science parlance.

@@

Although a family of more and more precise quantum IVPMs might be
induced from a real quantum state, given a particular quantum IVPM,
i.e., using a particular measurement apparatus, our investigation
leaves an open question of whether behind it there exists a ``real''
state. Despite the possibility to use quantum IVPMs as the most primitive
definition of states, we might focus on the meaning of the probability.
Since a quantum IVPM cannot be defined without consider a particular
measurement apparatus, and the information extracted from this apparatus,
the interval-valued probability itself could be considered subjective,
and could be interpreted in the Bayesian sense as ``lack of knowledge''.
This, and similar arguments elegantly expressed by recent work on
Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which
suggests that the quantum state is more like an interactive system
in computer science parlance. In other words, the state is only determined
by its interactions with the environment or observers. A rough but
useful analogy in the context of computer science would be a web server:
the state of such a system cannot be said to exist independently of
the interactions with clients; each interaction with a client determines
a future state of the system and may affect future interactions. Crucially,
each client may have a \emph{different} view of the web server that
is consistent with their own history of interactions. This computational
perspective agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
that asserts that the quantum state is subjective: each observer has
a different view of the quantum system that is consistent with their
previous observations and that allows that observer, independently
of other observers, to assign beliefs (i.e., probabilities) to possible
future interactions.
